Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-02 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:02	16:35:00	(Fri 2.Oct)

\author{Jo~Inge~Buskenes, %
        Roy~Edgar~Hansen, %
        Andreas~Austeng%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem All authors are with the Department
of Informatics, University of Oslo, Norway.}% <-this % stops a space

@@

This article is outlined as follows:

@@

\newpage
\subsection{Receive Beamforming}

@@

\section{MVDR}

@@

\section{LCA}

@@

The authors would like to thank Kongsberg Maritime, the Norwegian Defence Research Establishment (FFI), and Bundeswehr Technical Center for Ships and Naval Weapons Bundeswehr (WTD 71) for the equipment and effort needed to acquire data of the cross and Holmengraa, as well as for allowing us to use it.

>>>>

\author{Jo~Inge~Buskenes, %
        Roy~Edgar~Hansen, %
        Andreas~Austeng%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem All authors are with the Department of Informatics, University of Oslo, Norway.}%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem R.E.Hansen is also with The Norwegian Defense Research Establishment (FFI), Norway.}% <-this % stops a space

@@

This article is outlined as follows: In section \ref{beamforming} we introduce beamforming, \ref{mvdr} MVDR \ref{lca} LCA \ref{} \ref{} \ref{}

@@

\newpage
\subsection{Receive Beamforming}\label{beamforming}

@@

\section{MVDR}\label{mvdr}

@@

\section{LCA}\label{lca}

@@

The authors would like to thank Kongsberg Maritime, the Norwegian Defence Research Establishment (FFI), and Bundeswehr Technical Center for Ships and Naval Weapons, Maritime Technology and Research (WTD 71), for the equipment and effort needed to acquire data of the cross and Holmengraa, as well as for allowing us to use it.
